The Shape Matching Element Method for Meshless Animation of NURBs Models

### 2021-01-19 paper/sections/methods.tex
methods overview (commented out Tys methods)

\section{Methods}
Given a volumetric model composed of one or more NURBS surfaces, the surface of each surface is reconstructed using a set of control points $\textbf{p}$ and their associated weights $w$. Following D-NURBS \cite{10.1145/176579.176580}, we take our degrees of freedom (DOF) to be control points of the surfaces and produce displacements directly on these control points at each simulation step. We note that we used a simplified version of D-NURBS in which the weights are held constant throughout the simulation and find this not to be limiting \myworries{(feel like we'll need better justification than saying just this?)}. We represent the degrees of freedom for the $i$-th NURBS surface with $m$ control points as $\mathbf{q}_i = \left[ \mathbf{p}_1^T, \dots, \mathbf{p}_m^T \right]^T \in \mathbb{R}^{3m}$. From this definition, we write the DOF for the entire model as $\mathbf{q} = \left[ \mathbf{q}_i^T, \dots, \mathbf{q}_n^T \right]^T$ where $n$ is the number of NURBS surfaces for the model.

To evaluate the volumetric integrals in solid mechanics models, we require material points $\mathbf{X} \in \mathbb{R}^{3m}$ in the undeformed space that serve as integration points. Our shape matching element method enables us to evaluate the deformed positions of the material points strictly using positions defined on the boundary. Like in VEM, we fit a polynomial to each boundary primitive (NURBS in this case) describing its deformation. The fitting of these polynomials closely follows that of the Shape Matching \cite{10.1145/1073204.1073216} approach where we perform a least squares polynomial fit to the deformed boundary points. These boundary points are represented by sampled positions on each NURBS surface. Since each surface is associated with a single polynomial, we can construct a unique polynomial for some arbitrary point by blending these polynomials. Thus given some material point $\mathbf{X}_i$ we find it's corresponding deformed position $\mathbf{x}_i$ via a weighted combination of the polynomials. This permits us to build a general deformation map which we use to construct our equations of motion.

In the following sections, we will first review the simplified D-NURBS model used to form our generalized coordinates. We then present our shape matching algorithm for fitting polynomials to surfaces .... In section ... we next describe how to blend these surface polynomials to construct a general deformation map for material points. Section ... describes our strategy for selecting integration points in the volume through a raycasting approach. Finally, we formulate our equations of motions from a Lagrangian formulation.

\section{D-NURBS Model}
\myworries{TODO: Most of these matrices should be paranthesis matrices}
We provide a brief overview of the D-NURBS formulation presented in \cite{10.1145/176579.176580}. Our models in our method are composed of a collection of NURBS surfaces.

\subsection{D-NURBS Formulation}
A point on a NURBS surface is typically expressed in the following form
\begin{equation}
\label{eqn:nurbs_srf}
    \mathbf{x}(u,v) = \frac{\sum_{i=1}^{n}\sum_{j=1}^{m}  \mathbf{p}_{i,j} w_{i,j} B_{i,k}(u)B_{j,l}(v)}
    {\sum_{i=1}^{n}\sum_{j=1}^{m} w_{i,j} B_{i,k}(u)B_{j,l}(v)}
    \text{,}
\end{equation}
where where have a total of $nm$ control points $\mathbf{p}$ and weights $w$. Using the B-spline basis functions and the weighted control points, this formula gives a map from our parametric coordinates $u,v$ to their corresponding position on the surface in $\mathbb{R}^{3m}$. $B_{i,k}(u)$ is the B-spline basis function for the $i-th$ control point with degree $k-1$.

We would like our generalized coordinates to be the control points of the model so that the dynamics operates directly on the original representation. Therefore, we would like to rewrite equation \ref{eqn:nurbs_srf} in the form
\begin{equation}
    \mathbf{x}(u,v) = \mathbf{J}(u,v)\mathbf{q}
    \text{,}
\end{equation}
where $\mathbf{q} = \left[ \mathbf{p}_{1,1}^T, \dots, \mathbf{p}_{i,j}^T, \dots, \mathbf{p}_{n,m}^T \right]^T \in \mathbb{R}^{3nm}$ is the set of $nm$ control points \myworries{in the overview I just write $n$ control points, but here i'm writing $nm$} for a single NURBS surface arranged as a column vector. $\mathbf{J} \in  \mathbb{R}^{3 x 3nm}$ is the NURBS jacobian that maps $(u,v)$ coordinates to world positions in $\mathbb{R}^{3}$.

The NURBS jacobian, $\mathbf{J}$, is a matrix composed of horizontally concatenated $3x3$ blocks where the $(i,j)$-th block is $\frac{\partial \mathbf{x}}{\partial \mathbf{p}_{i,j}}$ for the $(i,j)$-th control point. $\frac{\partial \mathbf{x}}{\partial \mathbf{p}_{i,j}}$ is a diagonal $3x3$ matrix where each diagonal entry $N_{i,j}(\mathbf{u})$ takes the form

\begin{equation}
\label{eqn:jacobian_diagonal}
    N_{i,j}(u,v)
    = \frac{w_{i,j} B_{i,k}(u)B_{j,l}(v)}{\sum_{i=1}^{n}\sum_{j=1}^{m} w_{i,j} B_{i,k}(u)B_{j,l}(v)}
    \text{.}
\end{equation}
Thus the NURBS jacobian for a single $(u,v)$ pair is written as
\begin{equation}
\label{eqn:uv_jacobian}
    \mathbf{J}(u,v) =
    \left[ \frac{\partial \mathbf{x}}{\partial \mathbf{p}_{1,1}} \dots
           \frac{\partial \mathbf{x}}{\partial \mathbf{p}_{i,j}} \dots 
           \frac{\partial \mathbf{x}}{\partial \mathbf{p}_{n,m}}
    \right]
    \text{.}
\end{equation}

This formulation is a simplification of the full D-NURBS described in \cite{10.1145/176579.176580} the weights of the NURBS are fixed throughout the simulation. Permitting the dynamics to modify weights would likely improve the expressiveness of the kinematics, but we find fixing the weights affords sufficiently expressive results and improves performance. The performance improvement is a result of having fixed $N_{i,j}(u,v)$ entries over the course of the simulation. The full D-NURBS model requires rebuilding the jacobian and consequently the mass matrices at each time step.

\subsection{Generalized Coordinates for a NURBS model}
The above formulation describes developing the map from a single $(u,v)$ coordinate to its corresponding position on the surface. In our simulation we represent the entire boundary of the NURBS model, so we require samples along each surface. We emphasize that we only require an initial selection of $(u,v)$ coordinates across each surface and the dynamics of the simulation modifies the set of control points $\mathbf{q}$ to modify the world space maps $\mathbf{x}(u,v)=\mathbf{J}(u,v)\mathbf{q}$.

Let's say for a NURBS surface on the model the DOF column vector is $\mathbf{q}_i$, which is the subset of control points in the generalized coordinates for the $i$-th surface. For a given surface with $m$ pairs of $\mathbf{u}=(u,v)$ coordinates sampled in parametric space, we write the jacobian for the $i$-th surface as \myworries{(should I use something like $\hat{\mathbf{J}}$ instead?)}
\begin{equation}
\label{eqn:surface_jacobian}
    \mathbf{J}_i =
    \left[ \mathbf{J}(\mathbf{u})_1^T \dots \mathbf{J}(\mathbf{u})_m^T \right]^T
    \text{.}
\end{equation}
Then if $\mathbf{x}_i$ is the set of $m$ world space positions for the $i$-th surface, we may write $\mathbf{x}_i = \mathbf{J}_i \mathbf{q}_i$. Finally, given the full set of generalized coordinates $\mathbf{q} = \left[ \mathbf{q}_i^T, \dots, \mathbf{q}_n^T \right]^T$ with $n$ surfaces, we may write jacobian $\mathbf{J}$ for the entire model as a block diagonal matrix:
\begin{equation}
\mathbf{J} = \left[ \begin{array}{ccccc}
\mathbf{J}_1 &  &  &  &  \\
 & \ddots &  &  &  \\
 &  & \mathbf{J}_i & &  \\
 &  &  & \ddots &  \\
 &  &  &  & \mathbf{J}_n \\
\end{array} \right]
\text{.}
\end{equation}
With this equation, the full set of world positions of the NURBS model may be written as $\mathbf{x} = \mathbf{J}\mathbf{q} \in \mathbb{R}^{3N}$ where $N$ is the total number of $(u,v)$ coordinates.

\section{Shape Matching}
The key feature of our method is its unique deformation map $\phi(\mathbf{X}) = \mathbf{x}$ mapping some arbitrary undeformed material point $\mathbf{X}$ to its corresponding deformed position in space $\mathbf{x}$. We develop this similarly to the VEM approach in that we say the function we intend to reproduce may be some highly nonlinear one, but it may be approximated accurately by a polynomial. Thus we seek some $\phi$ function where  $\phi^* \approx \phi$ where $\phi^*$ is the true solution. In $1$-D this means we wish to find a function of the form $\phi(X) = c_1 + c_2X + c_3X^2 + \dots + c_nX^{n-1}$ where each $c_i$ is an unknown polynomial coefficient and the $X^i$ terms are elements of the polynomial basis.

\subsection{The Shape Matching Element}
In typical FEM in graphics, we make use of tetrahedral or triangular elements with a piecewise-linear function space. In such a case our functions may be evaluated as a weighted combination of the nodal values of an element: $f(\mathbf x)=\sum_{i=0}^n f_i \phi_i(\mathbf{x})$ where $n$ is the number of nodal values and $\phi_i$ is the i-th barycentric coordinates. Thus in this case we have the simple deformation map $\mathbf{x(X)} = \sum_{i=0}^n \mathbf{x}_i \phi_i(\mathbf{X})$. However, our method contrasts this typical approach in that our elements are more general and take the form of any arbitrary boundary primitive, such as NURBS, and also that the function space in non-linear.

In our algorithm, a single shape matching element is represented by a NURBS surface, a center of mass, and polynomial describing its current deformation. We construct these polynomials via a shape matching strategy. With the addition of the center of mass, we describe the shapes deformation about this point and thus the monomial basis in the case of a linear polynomial is $\left[ \mathbf 1^T (\mathbf{X - \bar{X}})^T \right]$ where $\mathbf 1^T$ is a constant $1$ column vector and $\mathbf{\bar{X}}$ is the center of mass for the element. To simplify the following formulas, we collect the non-constant terms of the monomial basis into a single vector $\mathbf{m}(\mathbf{X}-\mathbf{\bar{X}})$. For example if $\mathbf{X} = (X,Y,Z)$, $\mathbf{\bar{X}} = (\bar X, \bar Y, \bar Z)$, and $\mathbf{q}=\mathbf{X}-\mathbf{\bar{X}}$ with a quadratic polynomial we would have
\begin{equation}
m(\mathbf{q)} = (
					q_1, q_2, q_3,
                   	q_1^2, q_2^2, q_3^3,
                   	q_1 q_2, q_2 q_3
                ) \in \mathbb{R}^k
                \text{,}
\end{equation}
where $k$ is the size of the monomial basis. Next we arrange this basis into a matrix of the form
\begin{equation}
\mathbf{M}(\mathbf{q}) = \left[ \begin{array}{ccc}
\mathbf{m}(\mathbf{q}) &  &  \\
 & \mathbf{m}(\mathbf{q})  &  \\
 &  & \mathbf{m}(\mathbf{q})  \\
\end{array} \right] \in \mathbb{R}^{3x3k}
\text{.}
\end{equation}
With this definition of the monomial basis, we may reconstruct the deformed position $\mathbf{x}$ for some material point $\mathbf{X}$ with
\begin{equation}
\mathbf{x}(\mathbf{X}) = \left[\mathbf{M}(\mathbf{X-\bar{X}}) \quad \mathbf{I} \right]
\left[ \begin{array}{c}
\mathbf{c} \\
\mathbf{t} \\
\end{array} \right]
\text{,}
\end{equation}
where $\mathbf{c} \in \mathbb{R}^{3k}$ is the set of polynomial coefficients for the non-constant terms, $\mathbf{t} \in \mathbb{R}^3$ is the constant term coefficients, and $\mathbf{I} \in \mathbb{R}^{3x3}$ is an identity matrix. The reason for separating out the constant term becomes more evident when we examine case where we have multiple elements.

The remaining step in defining a single element is to describe how to solve for the polynomial coefficients. For a single element, we have $n$ material points $(\mathbf{X}_1 \dots \mathbf{X}_n)$ and their corresponding deformed positions $(\mathbf{x}^*_1 \dots \mathbf{x}^*_n)$. As these elements are defined on a boundary, these are both known throughout the simulation. Therefore we may form a fitting problem to solve for the polynomial coefficients that minimize the error $\sum_i^n ||\mathbf{x}_i^* - \mathbf{X}_i ||^2$.  We minimize this error in a least squares sense where we first form the system
\begin{equation}
\left[\begin{array}{c}
\mathbf{M}(\mathbf{X_1-\bar{X}}) \quad \mathbf{I} \\
\vdots \\
\mathbf{M}(\mathbf{X_i-\bar{X}}) \quad \mathbf{I} \\
\vdots \\
\mathbf{M}(\mathbf{X_n-\bar{X}}) \quad \mathbf{I} \\
\end{array} \right]
\left[ \begin{array}{c}
\mathbf{c} \\
\mathbf{t} \\
\end{array} \right] = 
\left[ \begin{array}{c}
\mathbf{x}_1^* \\
\vdots \\
\mathbf{x}_i^* \\
\vdots \\
\mathbf{x}_n^*
\end{array} \right]
\text{,}
\end{equation}
and then in the more compact form
\begin{equation}
\label{eqn:fitting_one}
\left[
\mathbf{A} \quad \mathbf{S}
\right]
\left[ \begin{array}{c}
\mathbf{c} \\
\mathbf{t} \\
\end{array} \right] = \mathbf{b}
\text{,}
\end{equation}
where $\mathbf{A}$ is the block containing the monomial matrices of the system, and $\mathbf{S}$ is the block of identity matrices. Next, to reduce the degrees of freedom of this system we let the deformed center of mass (the constant term coefficients), $t$, be equal to the mean of the deformed positions influenced by this center of mass. In the case of one element we have $t = \frac{1}{n}\sum_i^n x_i^*$. We describe the details on center of mass selection in section \myworries{insert here}. In matrix form we have
\begin{equation}
\label{eqn:t_solution}
t = 
\underbrace{
\left[\begin{array}{ccccccc}
\frac{1}{n} & & \cdots \frac{1}{n} & & \\
& \frac{1}{n} & \cdots & \frac{1}{n} & \\
& & \frac{1}{n} \cdots & & \frac{1}{n} \\
\end{array} \right]}_{T} 
\mathbf{b}
\text{.}
\end{equation} (\myworries{spacing on this looks bad....}). Finally, this leaves us with the system
\begin{equation}
\mathbf{A}\mathbf{c}=(\mathbf{I}-\mathbf{ST})\mathbf{b}
\text{.}
\end{equation}
Like in the original Shape Matching \cite{10.1145/1073204.1073216}, we solve for the coefficients by minimizing the error in a least squares sense, resulting in
\begin{equation}
\label{eqn:c_one_element}
\begin{split}
\mathbf{c} & = (\mathbf{A}^T\mathbf{A})^{-1}\mathbf{A}^T(\mathbf{I-ST})\mathbf{b} \\
           & = \mathbf{L}\mathbf{b}
\end{split}
\text{.}
\end{equation}
This $\mathbf{L}$ matrix thus gives us our file ingredient in the element, coefficients defining the polynomial. We emphasize that $\mathbf{L}$ is constant throughout the simulation, therefore as $\mathbf{b}$ varies in the simulation, $\mathbf{Lb}$ gives us a new set of polynomial coefficients as $\mathbf{b}$ changes.

\subsection{Shape Matching with Multiple Elements}
In a typical simulation we will have multiple shape matching elements where the boundary of each element is defined by a different NURBS surface. Therefore for the entire model each shape has a boundary, a polynomial describing its deformation, as well as an associated center of mass. These centers of mass may not be distinct, meaning that a single center of mass may be shared among multiple surfaces. This sharing of center of masses is typical and in some cases required (\myworries{reference center of mass section that describes how for planar surfaces we need to share COM to get a COM out of plane}). This leads to a new definition of the center of mass where it is the mean of all the boundary points associated with it.

>>>>

\section{Overview}
The input to the Shape Matching Element Method (SEM)  is a NURBS \emph{boundary representation} of a volumetric object, along with a set of physical parameters 
(density, constitutive model, model parameters etc). The output is an elastodynamic simulation. 
SEM consists of preprocessing and runtime simulation phases~\refalg{sem} and at no point do we need to generate a volumetric mesh of the input. 
In the \emph{preprocessing} stage we use raycasting to find quadrature points and weights for volumetric integration, as well as to compute part blending parameters. 
Finally we construct local shape matching operators and construct the mass matrix for our problem.

At runtime we use standard time integration schemes to time step the system (we show linearly implicit, fully implicit, runge-kutta four). 
These require us to evaluate the energy, gradient and Hessian (implicit only) which we do at the previously computed quadrature points. 
For collisions we use penalty forces and apply them as external forces during integration.

\begin{algorithm}[h]
    \label{alg:sem}
    \SetAlgoLined
    \KwResult{Write here the result }
     initialization\;
     \While{While condition}{
      instructions\;
      \eIf{condition}{
       instructions1\;
       instructions2\;
       }{
       instructions3\;
      }
     }
     \caption{SEM Algorithm}
    \end{algorithm}
\section{Methods}

% \section{Methods}
% \dave{We should probably put some pseudo code for the preprocessing and the runtime algorithms right up fron, along with a quick textual walk through of the method.}
% Given a volumetric model composed of one or more NURBS surfaces, the surface of each surface is reconstructed using a set of control points $\textbf{p}$ and their associated weights $w$. Following D-NURBS \cite{10.1145/176579.176580}, we take our degrees of freedom (DOF) to be control points of the surfaces and produce displacements directly on these control points at each simulation step. We note that we used a simplified version of D-NURBS in which the weights are held constant throughout the simulation and find this not to be limiting \myworries{(feel like we'll need better justification than saying just this?)}. We represent the degrees of freedom for the $i$-th NURBS surface with $m$ control points as $\mathbf{q}_i = \left[ \mathbf{p}_1^T, \dots, \mathbf{p}_m^T \right]^T \in \mathbb{R}^{3m}$. From this definition, we write the DOF for the entire model as $\mathbf{q} = \left[ \mathbf{q}_i^T, \dots, \mathbf{q}_n^T \right]^T$ where $n$ is the number of NURBS surfaces for the model.

% To evaluate the volumetric integrals in solid mechanics models, we require material points $\mathbf{X} \in \mathbb{R}^{3m}$ in the undeformed space that serve as integration points. Our shape matching element method enables us to evaluate the deformed positions of the material points strictly using positions defined on the boundary. Like in VEM, we fit a polynomial to each boundary primitive (NURBS in this case) describing its deformation. The fitting of these polynomials closely follows that of the Shape Matching \cite{10.1145/1073204.1073216} approach where we perform a least squares polynomial fit to the deformed boundary points. These boundary points are represented by sampled positions on each NURBS surface. Since each surface is associated with a single polynomial, we can construct a unique polynomial for some arbitrary point by blending these polynomials. Thus given some material point $\mathbf{X}_i$ we find it's corresponding deformed position $\mathbf{x}_i$ via a weighted combination of the polynomials. This permits us to build a general deformation map which we use to construct our equations of motion.

% In the following sections, we will first review the simplified D-NURBS model used to form our generalized coordinates. We then present our shape matching algorithm for fitting polynomials to surfaces .... In section ... we next describe how to blend these surface polynomials to construct a general deformation map for material points. Section ... describes our strategy for selecting integration points in the volume through a raycasting approach. Finally, we formulate our equations of motions from a Lagrangian formulation.

% \section{D-NURBS Model}
% \myworries{TODO: Most of these matrices should be paranthesis matrices}
% We provide a brief overview of the D-NURBS formulation presented in \cite{10.1145/176579.176580}. Our models in our method are composed of a collection of NURBS surfaces.

% \subsection{D-NURBS Formulation}
% A point on a NURBS surface is typically expressed in the following form
% \begin{equation}
% \label{eqn:nurbs_srf}
%     \mathbf{x}(u,v) = \frac{\sum_{i=1}^{n}\sum_{j=1}^{m}  \mathbf{p}_{i,j} w_{i,j} B_{i,k}(u)B_{j,l}(v)}
%     {\sum_{i=1}^{n}\sum_{j=1}^{m} w_{i,j} B_{i,k}(u)B_{j,l}(v)}
%     \text{,}
% \end{equation}
% where where have a total of $nm$ control points $\mathbf{p}$ and weights $w$. Using the B-spline basis functions and the weighted control points, this formula gives a map from our parametric coordinates $u,v$ to their corresponding position on the surface in $\mathbb{R}^{3m}$. $B_{i,k}(u)$ is the B-spline basis function for the $i-th$ control point with degree $k-1$.

% We would like our generalized coordinates to be the control points of the model so that the dynamics operates directly on the original representation. Therefore, we would like to rewrite equation \ref{eqn:nurbs_srf} in the form
% \begin{equation}
%     \mathbf{x}(u,v) = \mathbf{J}(u,v)\mathbf{q}
%     \text{,}
% \end{equation}
% where $\mathbf{q} = \left[ \mathbf{p}_{1,1}^T, \dots, \mathbf{p}_{i,j}^T, \dots, \mathbf{p}_{n,m}^T \right]^T \in \mathbb{R}^{3nm}$ is the set of $nm$ control points \myworries{in the overview I just write $n$ control points, but here i'm writing $nm$} for a single NURBS surface arranged as a column vector. $\mathbf{J} \in  \mathbb{R}^{3 x 3nm}$ is the NURBS jacobian that maps $(u,v)$ coordinates to world positions in $\mathbb{R}^{3}$.

% The NURBS jacobian, $\mathbf{J}$, is a matrix composed of horizontally concatenated $3x3$ blocks where the $(i,j)$-th block is $\frac{\partial \mathbf{x}}{\partial \mathbf{p}_{i,j}}$ for the $(i,j)$-th control point. $\frac{\partial \mathbf{x}}{\partial \mathbf{p}_{i,j}}$ is a diagonal $3x3$ matrix where each diagonal entry $N_{i,j}(\mathbf{u})$ takes the form

% \begin{equation}
% \label{eqn:jacobian_diagonal}
%     N_{i,j}(u,v)
%     = \frac{w_{i,j} B_{i,k}(u)B_{j,l}(v)}{\sum_{i=1}^{n}\sum_{j=1}^{m} w_{i,j} B_{i,k}(u)B_{j,l}(v)}
%     \text{.}
% \end{equation}
% Thus the NURBS jacobian for a single $(u,v)$ pair is written as
% \begin{equation}
% \label{eqn:uv_jacobian}
%     \mathbf{J}(u,v) =
%     \left[ \frac{\partial \mathbf{x}}{\partial \mathbf{p}_{1,1}} \dots
%            \frac{\partial \mathbf{x}}{\partial \mathbf{p}_{i,j}} \dots 
%            \frac{\partial \mathbf{x}}{\partial \mathbf{p}_{n,m}}
%     \right]
%     \text{.}
% \end{equation}

% This formulation is a simplification of the full D-NURBS described in \cite{10.1145/176579.176580} the weights of the NURBS are fixed throughout the simulation. Permitting the dynamics to modify weights would likely improve the expressiveness of the kinematics, but we find fixing the weights affords sufficiently expressive results and improves performance. The performance improvement is a result of having fixed $N_{i,j}(u,v)$ entries over the course of the simulation. The full D-NURBS model requires rebuilding the jacobian and consequently the mass matrices at each time step.

% \subsection{Generalized Coordinates for a NURBS model}
% The above formulation describes developing the map from a single $(u,v)$ coordinate to its corresponding position on the surface. In our simulation we represent the entire boundary of the NURBS model, so we require samples along each surface. We emphasize that we only require an initial selection of $(u,v)$ coordinates across each surface and the dynamics of the simulation modifies the set of control points $\mathbf{q}$ to modify the world space maps $\mathbf{x}(u,v)=\mathbf{J}(u,v)\mathbf{q}$.

% Let's say for a NURBS surface on the model the DOF column vector is $\mathbf{q}_i$, which is the subset of control points in the generalized coordinates for the $i$-th surface. For a given surface with $m$ pairs of $\mathbf{u}=(u,v)$ coordinates sampled in parametric space, we write the jacobian for the $i$-th surface as \myworries{(should I use something like $\hat{\mathbf{J}}$ instead?)}
% \begin{equation}
% \label{eqn:surface_jacobian}
%     \mathbf{J}_i =
%     \left[ \mathbf{J}(\mathbf{u})_1^T \dots \mathbf{J}(\mathbf{u})_m^T \right]^T
%     \text{.}
% \end{equation}
% Then if $\mathbf{x}_i$ is the set of $m$ world space positions for the $i$-th surface, we may write $\mathbf{x}_i = \mathbf{J}_i \mathbf{q}_i$. Finally, given the full set of generalized coordinates $\mathbf{q} = \left[ \mathbf{q}_i^T, \dots, \mathbf{q}_n^T \right]^T$ with $n$ surfaces, we may write jacobian $\mathbf{J}$ for the entire model as a block diagonal matrix:
% \begin{equation}
% \mathbf{J} = \left[ \begin{array}{ccccc}
% \mathbf{J}_1 &  &  &  &  \\
%  & \ddots &  &  &  \\
%  &  & \mathbf{J}_i & &  \\
%  &  &  & \ddots &  \\
%  &  &  &  & \mathbf{J}_n \\
% \end{array} \right]
% \text{.}
% \end{equation}
% With this equation, the full set of world positions of the NURBS model may be written as $\mathbf{x} = \mathbf{J}\mathbf{q} \in \mathbb{R}^{3N}$ where $N$ is the total number of $(u,v)$ coordinates.

% \section{Shape Matching}
% The key feature of our method is its unique deformation map $\phi(\mathbf{X}) = \mathbf{x}$ mapping some arbitrary undeformed material point $\mathbf{X}$ to its corresponding deformed position in space $\mathbf{x}$. We develop this similarly to the VEM approach in that we say the function we intend to reproduce may be some highly nonlinear one, but it may be approximated accurately by a polynomial. Thus we seek some $\phi$ function where  $\phi^* \approx \phi$ where $\phi^*$ is the true solution. In $1$-D this means we wish to find a function of the form $\phi(X) = c_1 + c_2X + c_3X^2 + \dots + c_nX^{n-1}$ where each $c_i$ is an unknown polynomial coefficient and the $X^i$ terms are elements of the polynomial basis.

% \subsection{The Shape Matching Element}
% In typical FEM in graphics, we make use of tetrahedral or triangular elements with a piecewise-linear function space. In such a case our functions may be evaluated as a weighted combination of the nodal values of an element: $f(\mathbf x)=\sum_{i=0}^n f_i \phi_i(\mathbf{x})$ where $n$ is the number of nodal values and $\phi_i$ is the i-th barycentric coordinates. Thus in this case we have the simple deformation map $\mathbf{x(X)} = \sum_{i=0}^n \mathbf{x}_i \phi_i(\mathbf{X})$. However, our method contrasts this typical approach in that our elements are more general and take the form of any arbitrary boundary primitive, such as NURBS, and also that the function space in non-linear.

% In our algorithm, a single shape matching element is represented by a NURBS surface, a center of mass, and polynomial describing its current deformation. We construct these polynomials via a shape matching strategy. With the addition of the center of mass, we describe the shapes deformation about this point and thus the monomial basis in the case of a linear polynomial is $\left[ \mathbf 1^T (\mathbf{X - \bar{X}})^T \right]$ where $\mathbf 1^T$ is a constant $1$ column vector and $\mathbf{\bar{X}}$ is the center of mass for the element. To simplify the following formulas, we collect the non-constant terms of the monomial basis into a single vector $\mathbf{m}(\mathbf{X}-\mathbf{\bar{X}})$. For example if $\mathbf{X} = (X,Y,Z)$, $\mathbf{\bar{X}} = (\bar X, \bar Y, \bar Z)$, and $\mathbf{q}=\mathbf{X}-\mathbf{\bar{X}}$ with a quadratic polynomial we would have

% \begin{figure}
%     \includegraphics[width=\columnwidth]{example-image-a}
%     \caption{Figure showing shape matching to NURBS}
%     \label{fig:shapematching}
% \end{figure}

% \begin{equation}
% m(\mathbf{q)} = (
% 					q_1, q_2, q_3,
%                    	q_1^2, q_2^2, q_3^3,
%                    	q_1 q_2, q_2 q_3
%                 ) \in \mathbb{R}^k
%                 \text{,}
% \end{equation}
% where $k$ is the size of the monomial basis. Next we arrange this basis into a matrix of the form
% \begin{equation}
% \mathbf{M}(\mathbf{q}) = \left[ \begin{array}{ccc}
% \mathbf{m}(\mathbf{q}) &  &  \\
%  & \mathbf{m}(\mathbf{q})  &  \\
%  &  & \mathbf{m}(\mathbf{q})  \\
% \end{array} \right] \in \mathbb{R}^{3x3k}
% \text{.}
% \end{equation}
% With this definition of the monomial basis, we may reconstruct the deformed position $\mathbf{x}$ for some material point $\mathbf{X}$ with
% \begin{equation}
% \mathbf{x}(\mathbf{X}) = \left[\mathbf{M}(\mathbf{X-\bar{X}}) \quad \mathbf{I} \right]
% \left[ \begin{array}{c}
% \mathbf{c} \\
% \mathbf{t} \\
% \end{array} \right]
% \text{,}
% \end{equation}
% where $\mathbf{c} \in \mathbb{R}^{3k}$ is the set of polynomial coefficients for the non-constant terms, $\mathbf{t} \in \mathbb{R}^3$ is the constant term coefficients, and $\mathbf{I} \in \mathbb{R}^{3x3}$ is an identity matrix. The reason for separating out the constant term becomes more evident when we examine case where we have multiple elements.

% The remaining step in defining a single element is to describe how to solve for the polynomial coefficients. For a single element, we have $n$ material points $(\mathbf{X}_1 \dots \mathbf{X}_n)$ and their corresponding deformed positions $(\mathbf{x}^*_1 \dots \mathbf{x}^*_n)$. As these elements are defined on a boundary, these are both known throughout the simulation. Therefore we may form a fitting problem to solve for the polynomial coefficients that minimize the error $\sum_i^n ||\mathbf{x}_i^* - \mathbf{X}_i ||^2$.  We minimize this error in a least squares sense where we first form the system
% \begin{equation}
% \left[\begin{array}{c}
% \mathbf{M}(\mathbf{X_1-\bar{X}}) \quad \mathbf{I} \\
% \vdots \\
% \mathbf{M}(\mathbf{X_i-\bar{X}}) \quad \mathbf{I} \\
% \vdots \\
% \mathbf{M}(\mathbf{X_n-\bar{X}}) \quad \mathbf{I} \\
% \end{array} \right]
% \left[ \begin{array}{c}
% \mathbf{c} \\
% \mathbf{t} \\
% \end{array} \right] = 
% \left[ \begin{array}{c}
% \mathbf{x}_1^* \\
% \vdots \\
% \mathbf{x}_i^* \\
% \vdots \\
% \mathbf{x}_n^*
% \end{array} \right]
% \text{,}
% \end{equation}
% and then in the more compact form
% \begin{equation}
% \label{eqn:fitting_one}
% \left[
% \mathbf{A} \quad \mathbf{S}
% \right]
% \left[ \begin{array}{c}
% \mathbf{c} \\
% \mathbf{t} \\
% \end{array} \right] = \mathbf{b}
% \text{,}
% \end{equation}
% where $\mathbf{A}$ is the block containing the monomial matrices of the system, and $\mathbf{S}$ is the block of identity matrices. Next, to reduce the degrees of freedom of this system we let the deformed center of mass (the constant term coefficients), $t$, be equal to the mean of the deformed positions influenced by this center of mass. In the case of one element we have $t = \frac{1}{n}\sum_i^n x_i^*$. We describe the details on center of mass selection in section \myworries{insert here}. In matrix form we have
% \begin{equation}
% \label{eqn:t_solution}
% t = 
% \underbrace{
% \left[\begin{array}{ccccccc}
% \frac{1}{n} & & \cdots \frac{1}{n} & & \\
% & \frac{1}{n} & \cdots & \frac{1}{n} & \\
% & & \frac{1}{n} \cdots & & \frac{1}{n} \\
% \end{array} \right]}_{T} 
% \mathbf{b}
% \text{.}
% \end{equation} (\myworries{spacing on this looks bad....}). Finally, this leaves us with the system
% \begin{equation}
% \mathbf{A}\mathbf{c}=(\mathbf{I}-\mathbf{ST})\mathbf{b}
% \text{.}
% \end{equation}
% Like in the original Shape Matching \cite{10.1145/1073204.1073216}, we solve for the coefficients by minimizing the error in a least squares sense, resulting in
% \begin{equation}
% \label{eqn:c_one_element}
% \begin{split}
% \mathbf{c} & = (\mathbf{A}^T\mathbf{A})^{-1}\mathbf{A}^T(\mathbf{I-ST})\mathbf{b} \\
%            & = \mathbf{L}\mathbf{b}
% \end{split}
% \text{.}
% \end{equation}
% This $\mathbf{L}$ matrix thus gives us our file ingredient in the element, coefficients defining the polynomial. We emphasize that $\mathbf{L}$ is constant throughout the simulation, therefore as $\mathbf{b}$ varies in the simulation, $\mathbf{Lb}$ gives us a new set of polynomial coefficients as $\mathbf{b}$ changes.

% \subsection{Shape Matching with Multiple Elements}
% In a typical simulation we will have multiple shape matching elements where the boundary of each element is defined by a different NURBS surface. Therefore for the entire model each shape has a boundary, a polynomial describing its deformation, as well as an associated center of mass. These centers of mass may not be distinct, meaning that a single center of mass may be shared among multiple surfaces. This sharing of center of masses is typical and in some cases required (\myworries{reference center of mass section that describes how for planar surfaces we need to share COM to get a COM out of plane}). This leads to a new definition of the center of mass where it is the mean of all the boundary points associated with it.
